Synthesizing Symmetric Lenses

### 2018-07-10 papers/SymmetricLenses/main.tex
in progress edits to section 1

To overcome this second difficulty, we turn to information theory 
to characterize the likely and unlikely lenses. 
We consider a ``likely'' lens to be one that propagates a lot of
information from source to 
target and vice versa. Conversely, an ``unlikely'' lens requires a
large amount of additional information to recover the target given a
source and vice versa.  
This categorization follows from the intuition
that users will typically want to synchronise formats with lots
of shared information, and so lenses that preserve 
more information are preferable.
To implement this
intuition, we turn to \emph{stochastic regular expressions}
(SREs)~\cite{?}, which simultaneously define a set of strings \`a la
regular expressions and a probability distribution over those
strings.  Using this information, we can calculate the shared
information content of two formats and our measure of
likeliness.

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic diagram for the simple symmetric lens synthesis
  algorithm. The user provides 
   regular expressions \BRegex and \BRegexAlt and a set of examples \Examples{}
    as input. \Expand first converts \BRegex and \BRegexAlt to
    stochastic regular expressions \Regex and \RegexAlt with default
    probabilities. It then finds pairs of stochastic regular expressions
    equivalent to \Regex and \RegexAlt and iteratively proposes them to \GreedySynth.
    \GreedySynth finds a lens typed between the supplied SREs.
    When the algorithm determines it has found a likely lens, it
  returns it.  \ksf{can we change the subscript on the returned lens
  to ``likely'' instead of ``best''? Also, is it the cost that is
  returned or the likeliness }
   }
  \label{fig:high-level-algorithm}
\end{figure}

@@

We implemented the \GreedySynth and \Expand algorithms and evaluated their
effectiveness of synthesizing synchronization functions on a range of
benchmarks, including data cleaning tasks taken from Flash Fill, information
extraction tasks taken from Augeas, and ad-hoc format synchronization tasks
taken from a variety of locations\footnote{The majority of these format
  synchronization tasks were found from the following index:
  \url{http://fileformats.archiveteam.org/wiki/Electronic_File_Formats}}.

In summary, our main contributions are:
\begin{itemize}
\item We define the space of simple symmetric lenses, which lies between
  asymmetric lenses and full symmetric lenses and has the useful property that
  its members don't have any internal state (\S\ref{sec:overview}). We describe
  a language for simple symmetric string lenses and the cost metric for that
  language (\S\ref{sec:ssl}).
\item We show how to synthesize simple symmetric lenses (including all
  asymmetric lenses as a special case), using a novel application of stochastic
  regular expressions to guide the search process (\S\ref{sec:synthesis}). In
  particular, we show that the RE star semi-ring equivalences remain valid when
  their semantics are enriched by distributions (\S\ref{sec:sre}).
\item We extend the Boomerang implementation with simple symmetric lenses,
  showing that they can easily be combined with a rich variety of other lens
  extensions including quotients and matching lenses. We evaluate our
  implementation over a set of benchmarks drawn from data cleaning, information
  extraction, and file synchronization tasks and demonstrate that we can
  synthesize all of them in under half a minute (\S\ref{sec:evaluation}).
%
  We also analyze the gap between simple and full symmetric lenses
  empirically and argue that simple ones suffice for many applications.
\item We show that the class of simple lenses can be characterized semantically
  as the subset of full symmetric lenses for which a simple ``forgetfulness''
  property holds (\S\ref{sec:relationship}).
\end{itemize}
We finish the paper with a discussion of related work (\S\ref{sec:related}) and
our final thoughts (\S\ref{sec:conc}).

>>>>

To overcome this second difficulty, we turn to information theory 
to characterize the likely and unlikely lenses. 
We consider a ``likely'' lens to be one that propagates a lot of
information from source to 
target and vice versa. Conversely, an ``unlikely'' lens requires a
large amount of additional information to recover the target given a
source and vice versa.  
This categorization follows from the intuition
that users will typically want to synchronise formats with lots
of shared information, and so lenses that preserve 
more information are preferable.
To implement this
intuition, we turn to \emph{stochastic regular expressions}
(SREs)~\cite{stoch-rnn,stoch-def}, which simultaneously define a set of strings \`a la
regular expressions and a probability distribution over those
strings.  Using this information, we can calculate the shared
information content of two formats and our measure of
likeliness.

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic diagram for the simple symmetric lens synthesis
  algorithm. The user provides 
   regular expressions \BRegex and \BRegexAlt and a set of examples \Examples{}
    as input. \Expand first converts \BRegex and \BRegexAlt to
    stochastic regular expressions \Regex and \RegexAlt with default
    probabilities. It then finds pairs of stochastic regular expressions
    equivalent to \Regex and \RegexAlt and iteratively proposes them to \GreedySynth.
    \GreedySynth finds a lens typed between the supplied SREs.
    When the algorithm determines it has found a likely lens, it
  returns it.  \ksf{Can we change cost to likeliness?}
   }
  \label{fig:high-level-algorithm}
\end{figure}

@@

We implemented the \GreedySynth and \Expand algorithms and evaluated their
effectiveness at synthesizing lenses on a range of
benchmarks, including data cleaning tasks taken from Flash Fill~\cite{gulwani-popl-2014}, information
extraction tasks taken from Augeas~\cite{Augeas}, and ad-hoc format synchronization tasks
taken from a variety of other locations\footnote{The majority of these format
  synchronization tasks were found from the following index:
  \url{http://fileformats.archiveteam.org/wiki/Electronic_File_Formats}}.

In summary, our main contributions are:
\begin{itemize}
\item We define simple symmetric lenses, which 
  have the useful property that they do not maintain any hidden state
  (\S\ref{sec:overview}).  
  We describe a language for defining them and describe how to
  calculate the likelihood of a  particular lens (\S\ref{sec:ssl}). 
  We show simple symmetric lenses
  fall between asymmetric lenses~\cite{Focal2005-long2} and full
  symmetric lenses~\cite{symmetric-lenses} in expressiveness (\S\ref{sec:related}). 
\item We show how to synthesize simple symmetric lenses (including all
  asymmetric lenses as a special case), using a novel application of stochastic
  regular expressions to guide the search process (\S\ref{sec:synthesis}). In
  particular, we show that the star semi-ring equivalences on regular
  expressions remain valid
  their semantics are enriched by distributions (\S\ref{sec:sre}).
\item We extend the Boomerang implementation with simple symmetric lenses,
  showing that they can easily be combined with a rich variety of other lens
  extensions including quotients and matching lenses. We evaluate our
  implementation over a set of benchmarks drawn from data cleaning, information
  extraction, and file synchronization tasks and demonstrate that we can
  synthesize all of them in under half a minute (\S\ref{sec:evaluation}).
%
  We also analyze the gap between simple and full symmetric lenses
  empirically and argue that simple ones suffice for many applications.
\item We show that the class of simple lenses can be characterized semantically
  as the subset of full symmetric lenses for which a simple ``forgetfulness''
  property holds (\S\ref{sec:relationship}).
\end{itemize}
We finish the paper with a discussion of related work (\S\ref{sec:related}) and
our final thoughts (\S\ref{sec:conc}).
